RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-01 manuscripts/manuscript.Rmd
Parked paragraph deleted from earlier text.

>>>>

Much richer metadata annotation is possible. Later we illustrate how
metadata annotation can be used to extend the base NeXML format to
represent new forms of data while maintaining compatibility with any
NeXML parser. The `RNeXML` package can be easily extended to support
helper functions such as `taxize_nexml` to add additional metadata
without imposing a large burden on the user.
